---
title: "Lab_4B"
output: html_document
author: Alina Sequeira
date: September 19, 2020
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

```{r}
report_03_11_2020 <-   read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-11-2020.csv")) %>%
  rename(Country_Region = "Country/Region", Province_State = "Province/State")
```
```{r}
str(report_03_11_2020)
```
```{r}
view(report_03_11_2020)
```

## Exercise 1
```{r}
report_09_13_2020 <-   read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/09-13-2020.csv"))
```
```{r}
str(report_09_13_2020)
```
```{r}
view(report_09_13_2020)
```

## Counts of Confirmed Cases and Deaths by Country (03-11-20)
```{r}
report_03_11_2020 %>% 
  group_by(Country_Region) %>% 
  summarize(Confirmed_Cases = sum(Confirmed), Total_Deaths = sum(Deaths)) 
```

## Counts of Confirmed Cases & Deaths by Country (09-13-20)
```{r}
report_09_13_2020 %>% 
  group_by(Country_Region) %>% 
  summarize(Confirmed_Cases = sum(Confirmed), Total_Deaths = sum(Deaths)) 
```

## Counts of Confirmed Cases by State (03-11-20)
```{r}
report_03_11_2020 %>% 
  filter(Country_Region == "US") %>%
  group_by(Province_State) %>% 
  summarize(Confirmed_Cases = sum(Confirmed))
```

## Counts of Confirmed Cases by State (09-13-20)
```{r}
report_09_13_2020 %>% 
  filter(Country_Region == "US") %>%
  group_by(Province_State) %>% 
  summarize(Confirmed_Cases = sum(Confirmed))
```

## Top 10 Countries for Death (03-11-20)
```{r}
report_03_11_2020 %>% 
  group_by(Country_Region) %>% 
  summarize(Total_Deaths = sum(Deaths)) %>% 
  arrange(desc(Total_Deaths)) %>% 
  slice(1:10)
```

## Top 10 Countries for Death (09-13-20)
```{r}
report_09_13_2020 %>% 
  group_by(Country_Region) %>% 
  summarize(Total_Deaths = sum(Deaths)) %>% 
  arrange(desc(Total_Deaths)) %>% 
  slice(1:10)
```

## Exercise 2
```{r}
report_0311_Deaths <- report_03_11_2020 %>% 
  group_by(Country_Region) %>% 
  summarize(Total_Deaths = sum(Deaths)) %>% 
  arrange(desc(Total_Deaths)) %>% 
  slice(1:10)
```
```{r}
ggplot(data = report_0311_Deaths, mapping = aes(x = Country_Region, y = Total_Deaths)) + 
  geom_point(color = "tomato")
```

## Plot - Top 10 Countries with Total Confirmed Cases (03-11-20)
```{r}
report_0311_Confirmed <- report_03_11_2020 %>% 
  group_by(Country_Region) %>% 
  summarize(Confirmed_Cases = sum(Confirmed)) %>% 
  arrange(desc(Confirmed_Cases)) %>% 
  slice(1:10)
```
```{r}
ggplot(data = report_0311_Confirmed, mapping = aes(x = Country_Region, y = Confirmed_Cases)) + 
  geom_point(color = "tomato")
```

## Plot - Top 10 Countries with Total Deaths (09-13-20)
```{r}
report_0913_Deaths <- report_09_13_2020 %>% 
  group_by(Country_Region) %>% 
  summarize(Total_Deaths = sum(Deaths)) %>% 
  arrange(desc(Total_Deaths)) %>% 
  slice(1:10)
```
```{r}
ggplot(data = report_0913_Deaths, mapping = aes(x = Country_Region, y = Total_Deaths)) + 
  geom_point(color = "steelblue") 
```

## Plot - Top 10 Countries with Total Confirmed Cases (09-13-20)
```{r}
report_0913_Confirmed <- report_09_13_2020 %>% 
  group_by(Country_Region) %>% 
  summarize(Confirmed_Cases = sum(Confirmed)) %>% 
  arrange(desc(Confirmed_Cases)) %>% 
  slice(1:10)
```
```{r}
ggplot(data = report_0913_Confirmed, mapping = aes(x = Country_Region, y = Confirmed_Cases)) + 
  geom_point(color = "steelblue")
```

## Bar Graph - Top 10 States with Confirmed Cases (03-11-20)
```{r}
reportcon_US311 <- report_03_11_2020 %>% 
  filter(Country_Region == "US") %>%
  group_by(Province_State) %>% 
  summarize(Confirmed_Cases = sum(Confirmed)) %>% 
  arrange(desc(Confirmed_Cases)) %>% 
  slice(1:10)
```
```{r}
ggplot(data = reportcon_US311, mapping = aes(x = Confirmed_Cases, y = Province_State )) + 
  geom_bar(stat = "identity", fill = "tomato")
```

## Bar Graph - Top 10 States with Deaths (03-11-20)
```{r}
reportdeath_US311 <- report_03_11_2020 %>% 
  filter(Country_Region == "US") %>%
  group_by(Province_State) %>% 
  summarize(Total_Deaths = sum(Deaths)) %>% 
  arrange(desc(Total_Deaths)) %>% 
  slice(1:10)
```
```{r}
ggplot(data = reportdeath_US311, mapping = aes(x = Total_Deaths, y = Province_State )) + 
  geom_bar(stat = "identity", fill = "tomato")
```

## Bar Graph - Top 10 States with Confirmed Cases (09-13-20)
```{r}
reportcon_US913 <- report_09_13_2020 %>% 
  filter(Country_Region == "US") %>%
  group_by(Province_State) %>% 
  summarize(Confirmed_Cases = sum(Confirmed)) %>% 
  arrange(desc(Confirmed_Cases)) %>% 
  slice(1:10)
```
```{r}
ggplot(data = reportcon_US913, mapping = aes(x = Confirmed_Cases, y = Province_State )) + 
  geom_bar(stat = "identity", fill = "steelblue")
```

## Bar Graph - Top 10 States with Deaths (09-13-20)
```{r}
reportdeath_US913 <- report_09_13_2020 %>% 
  filter(Country_Region == "US") %>%
  group_by(Province_State) %>% 
  summarize(Total_Deaths = sum(Deaths)) %>% 
  arrange(desc(Total_Deaths)) %>% 
  slice(1:10)
```
```{r}
ggplot(data = reportdeath_US913, mapping = aes(x = Total_Deaths, y = Province_State )) + 
  geom_bar(stat = "identity", fill = "steelblue")
```

